Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-03 Grassmannian_cells.tex

For general $m\geq 1$, we will see that every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ corresponds to a basis element of $\Ext(\tilde P_{m+1}^{[n-1]},\tilde P_m)$. If the subquivers $\Gamma(1)$ and $\Gamma(2)$ have precisely one source and precisely one sink respectively, the $2$-arrow corresponds to a unique arrow of the original quiver $K(n)$ as every arrow of the universal covering does. In these cases, we label the $2$-arrow by the corresponding arrow.
\item The following two remarks are meant to understand the structure of the $2$-quivers. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
\[
  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
\]

@@

\item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
\begin{align}\label{eq:homext} \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}. \tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).\end{align}
This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$. 
In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
\end{enumerate}
\end{remark}

>>>>

\item The following two remarks are meant to understand the structure of the $2$-quivers. Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
\[
  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
\]

@@

\item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
\begin{align}
  \label{eq:homext} 
  \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}. \tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).
\end{align}
This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$. 
In view of Corollary \ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
\end{enumerate}
\end{remark}
